Addition and removal energies of circular quantum dots

### 2017-06-13 Manuscript/paper.tex
Fix some missing refs + split \Ds

The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.\ \cite{kehreinflow2006,heikophysrep2016,lnp936} for derivations and calculational details.

@@

The sequence of transformations is parameterized by a continuous variable $s$ known as the \textit{flow parameter}.  Without loss of generality, we can define $s = 0$ to be the beginning of this sequence, thus $\hat{H}(0)$ is simply the original Hamiltonian.  At any value of $s$, the evolving Hamiltonian $\hat{H}(s)$ is related to the original Hamiltonian by
\begin{align*}
  \hat{H}(s) \equiv \hat{U}(s) \hat{H}(0) \hat{U}^\dagger(s),
\end{align*}
where $U(s)$ is a unitary operator that describes the product of all such transformations since $s = 0$.  Taking the derivative with respect to $s$, we obtain:
\begin{align*}
  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\Ds} \hat{H}(0) \hat{U}^\dagger(s) + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}.
\end{align*}
If we define an operator $\hat{\eta}(s)$ as
\begin{align} \label{eq:etadefinition}
  \hat{\eta}(s) \equiv \frac{\D \hat{U}(s)}{\D s} \hat{U}^\dagger(s),
\end{align}
we find that it is antihermitian as a result of the unitarity of $\hat{U}(s)$:
\begin{align*}
  \hat{\eta}(s) + \hat{\eta}^\dagger(s)
  = \frac{\D}{\D s} \left(\hat{U}(s) \hat{U}^\dagger(s)\right)
  = 0,
\end{align*}
From this property we can derive a differential equation known as the \textit{SRG flow equation}:
\begin{align} \label{eq:imsrgode}
  \frac{\D \hat{H}(s)}{\D s} = [\hat{\eta}(s), \hat{H}(s)].
\end{align}
This equation allows $\hat{H}(s)$ to be evaluated without explicitly constructing the full transformation $\hat U(s)$.  The focus is instead shifted to the operator $\hat \eta(s)$, the \textit{generator} of the transformation.  When $\hat \eta(s)$ is \emph{multiplicatively} integrated (\textit{product integral}), the full unitary transformation $\hat U(s)$ is recovered:
\begin{align} \label{eq:etaintegral}
  \hat U(s')
  = \lim_{\Delta s \to 0} \prod_{i = 1}^n \mathrm{e}^{\hat{\eta}(s_i) \Delta s},
\end{align}
where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.  This is the formal solution to the linear differential equation Eq.\ (\ref{eq:etadefinition}).  The product integral in Eq.\ (\ref{eq:etaintegral}) may also be reinterpreted as \textit{$s$-ordering} \cite{reimann2013quantum} in analogy to time-ordering from quantum field theory.

>>>>

The central theme of similarity renormalization group (SRG) methods is the application of a continuous sequence of unitary transformations on the Hamiltonian to evolve it into a band- or block-diagonal form, see for examples Refs.\ \cite{kehrein2006flow,Hergert2016165,lnp936} for derivations and calculational details.

@@

The sequence of transformations is parameterized by a continuous variable $s$ known as the \textit{flow parameter}.  Without loss of generality, we can define $s = 0$ to be the beginning of this sequence, thus $\hat{H}(0)$ is simply the original Hamiltonian.  At any value of $s$, the evolving Hamiltonian $\hat{H}(s)$ is related to the original Hamiltonian by
\begin{align*}
  \hat{H}(s) \equiv \hat{U}(s) \hat{H}(0) \hat{U}^\dagger(s),
\end{align*}
where $U(s)$ is a unitary operator that describes the product of all such transformations since $s = 0$.  Taking the derivative with respect to $s$, we obtain:
\begin{align*}
  \frac{\D}{\D s} \hat{H}(s) = \frac{\D \hat{U}(s)}{\D s} \hat{H}(0) \hat{U}^\dagger(s) + \hat{U}(s) \hat{H}(0) \frac{\D \hat{U}^\dagger (s)}{\D s}.
\end{align*}
If we define an operator $\hat{\eta}(s)$ as
\begin{align} \label{eq:etadefinition}
  \hat{\eta}(s) \equiv \frac{\D \hat{U}(s)}{\D s} \hat{U}^\dagger(s),
\end{align}
we find that it is antihermitian as a result of the unitarity of $\hat{U}(s)$:
\begin{align*}
  \hat{\eta}(s) + \hat{\eta}^\dagger(s)
  = \frac{\D}{\D s} \left(\hat{U}(s) \hat{U}^\dagger(s)\right)
  = 0,
\end{align*}
From this property we can derive a differential equation known as the \textit{SRG flow equation}:
\begin{align} \label{eq:imsrgode}
  \frac{\D \hat{H}(s)}{\D s} = [\hat{\eta}(s), \hat{H}(s)].
\end{align}
This equation allows $\hat{H}(s)$ to be evaluated without explicitly constructing the full transformation $\hat U(s)$.  The focus is instead shifted to the operator $\hat \eta(s)$, the \textit{generator} of the transformation.  When $\hat \eta(s)$ is \emph{multiplicatively} integrated (\textit{product integral}), the full unitary transformation $\hat U(s)$ is recovered:
\begin{align} \label{eq:etaintegral}
  \hat U(s')
  = \lim_{\Delta s \to 0} \prod_{i = 1}^n \mathrm{e}^{\hat{\eta}(s_i) \Delta s},
\end{align}
where $s_i \equiv i \Delta s$, $n \equiv \lfloor s' / \Delta s \rfloor$, and $\lfloor x \rfloor$ denotes the \textit{floor} of $x$.  This is the formal solution to the linear differential equation Eq.\ (\ref{eq:etadefinition}).  The product integral in Eq.\ (\ref{eq:etaintegral}) may also be reinterpreted as \textit{$s$-ordering} \cite{reimann2013quantum} in analogy to time-ordering from quantum field theory.
